Optimizing a PoS Tag Set for Dependency Parsing

### 2016-05-04 submission.tex
More refs to intro

\section{Introduction}
\label{sec:intro}
PoS tagging is an important preprocessing step for many NLP tasks,
such as parsing, named entity recognition and sentiment
analysis. Whereas much effort has gone into the development of
PoS-taggers, to the effect that this task is often considered more or
less a solved task, considerably less effort has been devoted to the
empirical evaluation of the PoS tag sets themselves. Error analysis of
PoS-taggers indicate that, whereas tagger improvement though means of
learning algorithm or feature engineering seems to have reached
something of a plateau, linguistic assessment of the distinctions made
by the PoS tag set may be a venue worth investigating further
\cite{Man:11}.  Clearly, the utility of a PoS tag set is tightly
coupled with the the downstream task for which it is performed. Even
so, PoS tag sets are usually employed in a ``one size fits all''
fashion, regardless of the requirements posed by the task which makes
use of this information.

>>>>

\section{Introduction}
\label{sec:intro}
PoS tagging is an important preprocessing step for many NLP tasks,
such as dependency parsing \cite{Niv:Hal:Kub:07,Haj:Cia:Joh:09}, named
entity recognition and sentiment analysis
\cite{Wil:Wie:Hof:09}. Whereas much effort has gone into the
development of PoS-taggers, to the effect that this task is often
considered more or less a solved task, considerably less effort has
been devoted to the empirical evaluation of the PoS tag sets
themselves. Error analysis of PoS-taggers indicate that, whereas
tagger improvement though means of learning algorithm or feature
engineering seems to have reached something of a plateau, linguistic
assessment of the distinctions made by the PoS tag set may be a venue
worth investigating further \cite{Man:11}.  Clearly, the utility of a
PoS tag set is tightly coupled with the the downstream task for which
it is performed. Even so, PoS tag sets are usually employed in a ``one
size fits all'' fashion, regardless of the requirements posed by the
task which makes use of this information.
